%-------------------------
% Resume in Latex
% Author: AlgoUniversity
%-------------------------

\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


% Page setup
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textbf{\small #3} & \textbf{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\usepackage{enumitem}
\setlist[itemize,1]{label=\textbullet, leftmargin=0.2in}
\setlist[itemize,2]{label=\textendash, leftmargin=0.2in}
\setlist[itemize,3]{label=$\cdot$, leftmargin=0.2in}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
{\Huge Pegah Fallah} \ \vspace{1pt}

\small \href{mailto:pegahfallah@outlook.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{pegahfallah@outlook.com}} ~
\href{https://linkedin.com/in/pegahf}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/pegahf}} ~
\href{http://www.pegahcode.com}{\raisebox{-0.2\height}\faGlobe\ \underline{www.pegahcode.com}} ~
\text{\small\raisebox{-0.1\height}\faPhone\ +971 58-6957278}
\vspace{-8pt}
\end{center}


%-----------SKILLS-----------
\section{Skills}
\resumeSubHeadingListStart
\item{
\small
\textbf{Programming Languages}: TypeScript, JavaScript, Python, Java, SQL, HTML/CSS, Node.js \\

\textbf{Frameworks \& Libraries}: React.js, Next.js, Express.js, Redux, Three.js, Web3.js, Vue.js, Tailwind CSS \\

\textbf{Backend \& Databases}: GraphQL, REST APIs, PostgreSQL, MySQL, Firebase \\

\textbf{DevOps \& Cloud}: AWS (Lambda, S3, EC2), Docker, CircleCI, GitHub Actions \\

\textbf{Tools \& Platforms}: Git, Jira, Confluence, Bitbucket, Trello, Agile/Scrum Methodologies \\

\textbf{Advanced Tools \& Concepts}: WebSockets, JWT, OAuth, Serverless Architecture, CI/CD Pipelines, Caching
}
\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{York University}{June 2023}
{BSc Computer Science}{Toronto, ON}
\resumeItemListStart
\resumeItem{Awards: Lassonde Scholarship (2021, 2022, 2023); IBM Changemaker Award (2023); YSpace Innovation Award (2023); Alexander Spasov Memorial Award (2021)}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------

\section{Work Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {Dubai Business Associates, Falcon \& Associates}{Sept 2024 -- Present}
  {Strategy Consulting Associate}{Dubai, UAE}
\resumeItemListStart
\resumeItem{Emirates Leisure Retail/MMI}
\begin{itemize}
    \item{Defined customer segments and CRM strategies for the MMI website and Costa Coffee loyalty app, increasing click-through rates by 20\%.}
    \item{Automated invoicing processes by building \textbf{Excel macros}, enabling the generation of 100 invoices in under 5 minutes.}
    \item{Performed\textbf{ A/B testing} to optimize custom audience segmentation, leading to a 25\% boost in ad engagement.}
    \item{Developed a \textbf{data pipeline} to streamline the integration of Insider CRM data, improving data accessibility for real-time KPI tracking using Power BI.}
    \item{Automated recurring reporting processes using \textbf{SQL, Python, and ETL workflows}, reducing reporting time.}
    \item{Developed \textbf{Power BI} dashboards to analyze customer spending trends and demonstrate the value of custom audiences, optimizing Meta campaign performance and identifying cost-saving opportunities.}
    \end{itemize}
\resumeItemListEnd

\resumeSubheading
{Deloitte}{Sept 2023 -- Sept 2024}
{Software Developer, Product Engineering}{Toronto, ON}
\resumeItemListStart
\resumeItem{Developed a provincial application that consolidates 82 healthcare employee management systems into a single scalable solution.
  \begin{itemize}
     \item{Engineered a library of responsive and reusable components using \textbf{React, Typescript, Tailwind, and Storybook}, enhancing design consistency and saving the team 3 hours per week.}
    \item{Generated test suites with \textbf{Jest and Enzyme}, achieving 90\% code coverage across critical components to ensure robust application performance.}
    \item{Refined front-end by optimizing rendering with React.memo and implementing lazy loading, ensuring smooth interactions and a \textbf{94\% task completion rate} without user-reported blockers.}
    \item{Optimized user experience and SEO by adhering to \textbf{web accessibility standards}, achieving a Task Usability Testing score of 75\%.}
    
  \end{itemize}
}
\resumeItem{Engineered a pivotal website for a federal government agency, directly benefiting 180,000+ businesses across Canada.}
\begin{itemize}
    \item{Automated \textbf{AWS workflows} using \textbf{Node.js}, including resource provisioning and deployment pipelines, reducing operational overhead by 30\%.}
    \item{Developed user interfaces with \textbf{React, Redux, Javascript, Tailwind CSS, Node.js, and Webpack}, focusing on maintainability and scalability.}

\end{itemize}
\resumeItem{Utilized technical skills to author proposals, aligning solutions with client needs and helping secure a \$9 million contract.}

\resumeItemListEnd

\resumeSubheading
{Meta}{May 2022 -- Aug 2022}
{Technical Program Manager Intern - Developer Infrastructure}{Seattle, WA}
\resumeItemListStart
\resumeItem{Defined 15 success metrics for internal app size tools, and executed the development of a dashboard, guiding improvements in app health across Meta.}
\resumeItem{Scoped and managed priorities, risks, timelines, and resource requirements for the project over a 12-week period.}
\resumeItem{Enhanced collaboration by employing Agile methodologies, resulting in meeting 100\% of project deadlines.}
\resumeItem{Provided data-driven insights, shaping the formation of OKRs, leading to a significant increase in productivity in performance, reliability, and efficiency.}
\resumeItemListEnd

\resumeSubheading
{Honda}{May 2020 -- Aug 2021}
{Engineering Intern - IT Applications}{Alliston, ON}
\resumeItemListStart
\resumeItem{Facilitated a critical software migration project of over 500-line control processes through application configuration, QA testing, and Java debugging.}
\resumeItem{Led a middleware migration project that cut engine factory downtime by 11 minutes daily, saving over \$100,000 annually.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{Augmented Reality Creator}{}
{TikTok Effect House}{}
\resumeItemListStart
\resumeItem{Achieved over 18 billion views and 2 billion likes on filters, ranking in the top 1\% of AR creators on TikTok.}
\resumeItem{Developed campaigns reaching over 20 million impressions for multiple clients, consistently exceeding marketing targets.}
\resumeItem{Utilized visual scripting, linear algebra, shaders, and 3D modelling to create captivating and immersive AR effects.}
\resumeItemListEnd

\resumeSubheading
{Vagon.tech}{}
{Sustainable Carpooling Application}{}
\resumeItemListStart
\resumeItem{Built a website with a team of 4 within 32 hours, winning the Best Use of CockroachDB award at TOHacks.}
\resumeItem{Implemented a scalable, decoupled, 3-tier architecture with a Nuxt.js frontend, Golang JSON REST API and Firebase backend, CockroachDB on Google Cloud storage, and deployment on Docker.}
\resumeItemListEnd
\resumeSubHeadingListEnd


\end{document}
